---
title: "Untitled"
author: "Jingpeng"
date: "3/5/2022"
output:
  pdf_document: 
    latex_engine: xelatex
  html_document:
    df_print: paged
    
header-includes: \usepackage{float} \floatplacement{figure}{H}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tm)
library(dplyr)
# install.packages("SnowballC")
library(SnowballC)
# install.packages("wordcloud")
library(wordcloud)
# install.packages("topicmodels")
library(topicmodels)
# install.packages("tidytext")
library(tidytext)
# install.packages("reshape2")
library(reshape2)
library(ggplot2)
rm(list=ls())
setwd("/Users/hongjingpeng/Desktop/Machine\ Learning/Machine-Learning-2022W/PSet4")

```
**Question 2**

**a-c**

```{r Q2_a-c}
## create the circle function
circleFun = function(center = c(-1, 2), r = 2, npoints = 100){
    tt <- seq(0, 2*pi, length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}

## sketch the curve
data = circleFun(c(-1, 2), 2, npoints = 100)
ggplot(data,aes(x,y)) + 
  geom_path() +
  xlim(-4, 4) + 
  xlab("X1") +
  ylim(-2, 10) + 
  ylab("X2") +
  annotate("text", x = -1, y = 2, label = "<4") + 
  annotate("text", x = 0, y = 6, label= ">4") + 
  geom_point(aes(x = 0, y = 0), colour = 'blue', fill = NA, size = 2, shape = 21)+
  geom_point(aes(x = -1, y = 1), colour = 'red', fill = NA, size = 2, shape = 21)+ 
  geom_point(aes(x = 2, y = 2), colour = 'blue', fill = NA, size = 2, shape = 21)+ 
  geom_point(aes(x = 3, y = 8), colour = 'blue', fill = NA, size = 2, shape = 21)+ 
  coord_fixed()
```

**d.**

We can rewrite the non-linear boundary:
$$
(1+X_1)^2 +(2−X_2)^2 =4
$$
as
$$
1+2X_1-4X_2+X_1^2+X_2^2=0
$$
This boundary is linear in terms of $X_1$, $X_1^2$, $X_2$, and $X_2^2$.



**Question 4**
```{r Q4}
library(ISLR)
# install.packages('e1071')
library(e1071)
Auto = Auto
```

**a.**

Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.
```{r Q4_a}
Auto$mpg2 = ifelse(Auto$mpg>median(Auto$mpg), 1, 0) %>%
  as.factor()
```

**b.**
```{r Q4_b}
set.seed(1)
## cross validation
tune.out=tune(svm, mpg2~., data=Auto, kernel="linear",
              ranges=list(cost=c(0.001, 0.01, 0.1, 1, 5, 10, 100)))
summary(tune.out)
```
From the results above we find that `cost=1` results in the lowest cross-validation error rate. We can see that when `cost` is large, the margins will be narrow. The classifier will fit the training data well, which may have low bias but high variance. On the contrary, when `cost` is small, the margins will be wide, which may have low variance but high bias. `cost=1` can control the bias-variance trade-off best among these values. Now we use the best model obtained through cross-validation to make predictions.
```{r Q4_b prediction}
bestmod = tune.out$best.model
ypred = predict(bestmod, Auto)
table(predict = ypred, truth = Auto$mpg2)
```
**c**






